### 2017-04-01 paper/evaluation.tex
Fix evaluation

From the \numMedLong{} subjects, we found \pomMedLong{} \pomf{} files
where \numPomMatched{} of those files match one of the keywords
mentioned above.  From these \numPomMatched{} build filesi. The
\numPomMatched{} configurations are distributed across \numProjectsPar{} 
projects from our sample.
% 
% \emph{From these results we found that $\sim$51\% of medium and
% long-running projects do not use parallel features to run test
% suites.}\Mar{please make it consistent with research
% question}\Mar{explain this is over(under)-estimated...}

>>>>

From the \numMedLong{} subjects, we found \pomMedLong{} \pomf{} files.
The \numPomMatched{} configurations are distributed across \numProjectsPar{} projects from our sample.
% 
% \emph{From these results we found that $\sim$51\% of medium and
% long-running projects do not use parallel features to run test
% suites.}\Mar{please make it consistent with research
% question}\Mar{explain this is over(under)-estimated...}
